Rank Recovery

### 2020-11-15 output_scripts/rank_recovery.Rmd
correct typo with isi prediction, ranks the wrong way around and similarly look at the isi scores from fitting to all data.

To be completed.

@@

>>>>

Here we estimate the rankings from each model using data from the
first 15 days of events, and then compute the estimate I&SI scores
from using those ranks on the remaining held out data.

@@

We can similarly repeat this for fitting each model to all 
data and look at the estimated I&SI scores based on those
inferred rankings.

```{r compute isi total, results='hide'}
score_fits_all <- list()
source(here("lib","cleanData.R"))

data_path <- "../output/"

full_data <- readRDS(here("data","mice.RData"))
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

mini_wl_matrix <- function(df, num_mice = 12) {
  # to avoid issues with reordering the data
  df <- as.data.frame(df)
  mylevs <- 1:num_mice
  df[, 1] <- factor(df[, 1], levels = mylevs)
  df[, 2] <- factor(df[, 2], levels = mylevs)
  df$result <- 1
  m1 = stats::xtabs(result ~ ., data = df)
  m1
}

compute_isi_score <- function(win_loss_matrix, curr_ranking) {
  # this takes ranking from highest to lowest
  wl <- win_loss_matrix[curr_ranking,curr_ranking]
  n <- as.numeric(dim(wl)[1])
  m <- matrix(0, n, n)
  siind <- matrix(0, n, n)
  I = 0
  SI = 0
  for (j in 2:n) {
    for (i in 1:(j - 1)) {
      siind[j, i] = j - i
      siind[i, j] = j - i
      if (wl[j, i] == 0 & wl[i, j] == 0) {
        m[j, i] = 0
        m[i, j] = 0
      }
      else {
        if (wl[j, i] > wl[i, j]) {
          m[j, i] = 1
          m[i, j] = -1
        }
        if (wl[j, i] < wl[i, j]) {
          m[j, i] = -1
          m[i, j] = 1
        }
        if (wl[j, i] == wl[i, j]) {
          m[j, i] = 0.5
          m[i, j] = 0.5
        }
      }
    }
  }
  I = sum(lower.tri(m) * m == 1)
  SI = sum((lower.tri(m) * m == 1) * siind)

  list(I_score = I, SI_score = SI)
}

for(current_cohort in 1:10) {
  # current_cohort <- cohort_id
  print(paste("Cohort",current_cohort))

  training_day <- 15
  ## if I change this then I need to refit

  print(current_cohort)
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  return_df <- cleanObservationPeriod(current_cohort, clean_data)

  #### Fit M1 ####
  load(paste(data_path,cohort_names[current_cohort],
             "/cohort_hp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

  # highest to lowest

  rank_m1 <- rev(order(apply(sim_cohort_hp$f, 2, mean)))

  #### Predict M2 ####
  load(paste(data_path,cohort_names[current_cohort],
             "/cohort_dchp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))
  # highest to lowest
  rank_m2 <- rev(order(apply(sim_cohort_dchp$f, 2, mean)))

  #### Predict M3 ####
  load(paste(data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

  # highest to lowest
  rank_m3 <- rev(order(apply(sim_cohort_mmhp$f, 2, mean)))

  #### Predict Agg Ranking ####
  load(paste(data_path,cohort_names[current_cohort],
             "/agg_rank_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

  # highest to lowest
  rank_agg <- rev(order(apply(sim_agg_rank$x, 2, mean)))

  #### ISI Predict ####
  full_wl <- mini_wl_matrix(df = cbind(return_df$initiator,
                                        return_df$recipient))

  isi_train <- isi98(full_wl)
  isi_rank <- as.numeric(isi_train$best_order)

  #### glicko predict
  glick_df <- return_df %>% 
    mutate(id = row_number(), score = 1) %>%
    select(id, initiator, recipient , score)

  gl_ranks <- rev(order(gl_train$ratings$Rating))

  #### save this output ####

  ### need to make sure the isi ordering is correct here

  est_ranks <- tibble(isi_full = isi_rank,
                      agg_full = rank_agg,
                      glicko_full = gl_ranks,
                      m1_full = rank_m1,
                      m2_full = rank_m2,
                      m3_full = rank_m3)

  # full_wl <- mini_wl_matrix(cbind(return_df$initiator, return_df$recipient))
  # best_isi <- isi98(full_wl)
  # this is giving me the ranks correctly but am I mapping them
  # correctly for reordering the wl matrix?

  ###
  ## do I want order here?
  ###
  scores <- est_ranks %>% map_dfr(~ compute_isi_score(full_wl, .x))

  scores$model <- c("isi","agg", "glicko", "m1","m2","m3")
  # scores <- scores %>% add_row(tibble_row(I_score = best_isi$I, 
  #                              SI_score = best_isi$SI,
  #                              model = "test_isi"))

  score_fits_all[[current_cohort]] <- scores

}

```{r plot these isi scores}
score_fits_all %>%
  map(~as_tibble(.)) %>%
  bind_rows(.id="index") %>%
  mutate(ISI = I_score + SI_score) %>%
  ggplot(aes(model,ISI)) + geom_boxplot()
```
